\chapter{Conclusion}
The development methods used in this project led to a clear progression through the phases. Multiple iterations meant the group had to evaluate the current state of the solution and think of improvements to the design. The time schedule was modified during the project to better reflect the most important phase at that stage. There is no clear division of the project work as the group members have worked closely together.

In relation to the project scope the group has achieved a working central data collection unit referenced as the CDU. The CDU has a working PC interface. Multiple sensor nodes have been made with a functioning measurement system. The sensor nodes are powered by the bus. The two components of the system can successfully communicate using the custom power line communication bus. The group has achieved two way communication. 

With regards to the requirements specification the group has achieved the ability to save data entries correctly in memory. The requirement for power consumption will be a part of the further development phase along with the optimisation of the design.

The whole system has been build as a prototype on PCBs with discrete components. In addition to a PCB, the CDU uses an Explorer 16 development board. The sensor node utilises an Altera DE2 board.

The technology developed in this project is a communication system built on top of a current loop. It serves as a proof of concept that it is  possible to create a bus with a single wire daisy chaining multiple sensor nodes. The bus is stable and reliable. 
