\chapter{Project planning}
\textit{Udkast til projektplan, herunder beskrivelser af hvilke eksperimenter, teknologier mm der forventes udarbejdet i løbet af afgangsprojektet}\\

\section{Time schedule}
Måske

\section{Experiments}
Måling på fødder med temperatursensorer

\section{Techologies}
Hest

\section{Project organizing}
Herunder følger information omkring planlægning or organisering af projektet.
\subsection{Project flow}
Her indsættes projektflow bilederne fra visio samt beskrivelse.
\subsection{Meetings}
The project is divided into sprints of 1 week duration. This is to help ensure momentum and agility.\\
Supervisor meetings: A minimum of one per week, preferably the same weekday: suggestion Monday.\\
Daily group meetings: A minimum of 3 per week, preferably more. Suggestion: Thursday, Wednesday and Friday.
\subsubsection{Weekly supervisor meetings and agenda}
\begin{itemize}
\item Since last meeting
\item Next weeks goals
\item Workrelated subjects
\item Closing remarks
\end{itemize}
\subsubsection{Daily group meetings and agenda}
\begin{itemize}
\item What did I accomplish yesterday?
\item What will I do today?
\subitem $\circ$ Todays "Must-Win" battles?
\item What obstacles are impeding my progress?
\end{itemize}
\subsection{Work and task distribution}
All tasks and challenges related to the project must be noted on posted notes and hung on the project planning board. This board must be organized to help give an overview of the projects progress and future task.\\
Task distribution will, whenever possible, be allocated at the daily group meetings. It is at all times possible to ad tasks to the board.\\
\subsection{}
