\chapter{Architecture background}

\section{Solution summary}
The project solution offers a dedicated system which is able to accommodate the problem described in the project description. The system should also support extensions of the system. This could be pressure sensors, humidity sensors and more. Therefore this document offers a generic architecture able to support various extensions of the system.\\
The solution consists of a central data unit which can communicate with all sensors in the system. The sensors have an address-range so the central unit are able to automatically detect all sensors and types connected to the system. 

\section{Architectural goals}
The goal of the architecture is to make a structured overview of all aspects of the solution.\\
It should consider all problems in the design of the overall system and present a simple and effective solution to these.\\
Although these solutions must not limit the project in the  implementation.\\

\section{Constraints}
The system isn't able to be connected to sensors already in the market. This is due to the fact that this solution offers its own communication protocol.\\

\section{Considerations}
This section contains some of the considerations that led us towards narrowing down our design.
\subsection{DC Levels versus FSK}
Before anything could be designed for the communication layers we had to determine which technology that would suit the project. The group had previous experience with 2 different technologies: Logic levels(i2c, SPI and more) and Frequency Modulation(FSK, HART). A comparison was made to determine which one was most noise robust and which one had the largest implementation complexity.\\
Logic levels was easy to implement but was not really noise robust. Frequency Modulation was more complex to implement but was noise robust.\\
To obtain noise robustness with Logic levels, it must be implemented with current levels instead of voltage.\\
The low implementation complexity and the noise robustness of  current level communication made this ideal for the project.\\
We choose this technology for our communication.
